---
title: "RSyntext Vignette"
author: "Alexander Pak, Harjyot Kaur, Yenan Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RSyntext Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Package Info

RSyntext is a package that provides high level summary statistics for input text. Its functions are made to be robust and are written in such a way that special characters or outliers in the text will not break expected behaviour. Functions contain parameters that provide the ability to clean input text, remove stopwords, etc. 

## Included Functions

`text_summarize()` : Provides total word count, total sentence count, most common + least common words, average word length, and average number of words per sentence
`text_quality()` : Provides the number of spelling errors in input text, as well as the presence of toxic words
`text_grams()` : Provides the most frequent n-grams in input text


## Example Use Cases

Below are example inputs and outputs for RSyntext. 

```{r}
suppressWarnings(library(RSyntext))
```
```{r}
example <- "I don’t care what they’re going to say. Let the storm rage on. The cold never bothered me anyway."

knitr::kable(text_summarize(example))
```
```{r}
example2 <- "This str has words spelllll wrong. This string has a slag word shitty."

knitr::kable(text_quality(example2))
```
```{r}
example3 <- "You can stand under my umbrella, You can stand under my umbrella, Under my umbrella, Under my umbrella, Under my umbrella"

knitr::kable(text_grams(example3))
```

